From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/acl2020_main.tex
update Table 4 in Sec 5

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object, i.e.,~the name most humans would choose.  
Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that object classification models ``spontaneously'' learn good entry-level names and that they can be further finetuned via transfer learning. 
\sz{A short sentence on human-like errors?}
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose.  
Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that object classification models ``spontaneously'' learn good entry-level names and that they can be further finetuned via transfer learning. 
\sz{A short sentence on human-like errors?}
\end{abstract}

### 2019-12-09 papers/ACL2020/analysis.tex
update Table 4 in Sec 5

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  gt &  hit &  valid &  incorrect &  hit &  valid &  incorrect \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &      0.8 &      4.4 &   63.6 &     21.0 &     15.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &      0.8 &      9.6 &   60.7 &     20.8 &     18.5 \\
                \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &      0.0 &      5.5 &   72.9 &     14.0 &     13.1 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &      0.5 &     11.2 &   48.5 &     17.8 &     33.7 \\
     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &      0.5 &      9.9 &   57.0 &     15.2 &     27.8 \\
    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &      0.5 &      9.4 &   58.2 &     15.2 &     26.7 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &      0.8 &     10.6 &   49.9 &     18.1 &     32.1 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
\end{table*}

>>>>

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
 \midrule
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
\end{table*}
